Tor's Usability for Censorship Circumvention

### 2015-10-05 paper/circumvention-experiment.tex
merge

\noindent {\bfseries Overview}
{\color {red}
% test tor, test improvements, may do followups on demand, push changes.

% setting up the environment wrt interface paths.

%improve what is below:
For users to circumvent censorship in their resident countries, they will need
to configure Tor to set up a proxy, bridge, or both. There is a configuration
wizard to help guide users through setting up their connection, but our
hypothesis is that the average user will not easily be able to configure Tor
correctly in these adverse settings, as they require the user to provide IP
addresses of proxies or bridges to use. The goal of our experiment is to see
how successful users are at carrying out common browsing tasks in an
adversarial setting using Tor.}\\

\begin{figure*}[t]
  \centering
    \includegraphics[width=\textwidth]{../torconfig.png}
    \caption{This flow chart shows all of the possible paths taken through the
    Tor configuration interface. A state represents a window in the interface,
    with the exception of the leaves, which indicate the final action taken by
    the interface (``q'' for quit, ``s'' for success, and ``e'' for error). The
    transitions between the states indicate which user action causes that
    transition. The cause for error is can be found
\href{https://github.com/lindanlee/circumvention-ux-tor/blob/master/torconfig.dot}{here}.}
\end{figure*}

@@

\noindent {\bfseries Experiment Flow} 
The experiment begins with the participants being informed that they are in a
simulated censorship
environment, where some --- but not all --- websites are blocked. We will
instruct them to visit a non-blocked website and a blocked website on a
``standard'' browser (one that is not used for censorship circumvention, such
as Chrome, Safari, or Firefox) to illustrate the situation.
Then, the participants will find out the role they they will be playing in the study.
This role is that of a regular citizen, who is trying to visit blocked websites
for non-critical leisurely purposes,
and that there is a minimal chance of risk. This information is given
to achieve
consistency across participants: their behavior might be different if they were
visiting websites to accomplish a critical task, or if they knew that there
were great risks.

>>>>

\noindent {\bfseries Overview}
{\color {red}
%improve what is below:
For users to circumvent censorship in their resident countries, they will need
to configure Tor to set up a proxy, bridge, or both. There is a configuration
wizard to help guide users through setting up their connection, but

Our hypothesis is that the average user does not have knowledge
knowledge on how certain pluggable transports work, or to provide non-publicly listed IP
addresses bridges. Certain real-world censorship settings require the user to provide this
information during configuration, which will affect how successful users are at 
circumventing censorship using Tor. There are blogs in countries which have extensive
censorship on how to configure Tor correctly {\color {red} cite something}, and participants may 
receive additional informatio through word of mouth. Our study will measure if the configuration
interface successfully guides users to correctly configuring their browser, not accounting 
for any additional  information that a real user may have.}\\

\begin{figure*}[t]
\label{fig:interface}
  \centering
    \includegraphics[width=\textwidth]{../torconfig.png}
    \caption{This flow chart shows all of the possible paths taken through the
    Tor configuration interface. A state represents a window in the interface,
    with the exception of the leaves, which indicate the final action taken by
    the interface (``q'' for quit, ``s'' for success, and ``e'' for error). The
    transitions between the states indicate which user action causes that
    transition. The cause for error is can be found
\href{https://github.com/lindanlee/circumvention-ux-tor/blob/master/torconfig.dot}{here}.}
\end{figure*}

@@

\noindent {\bfseries Experiment Flow} 
We will run three sets of the experiment, the first set to test the current configuration
interface, a second set to test the improved interface, and a third set to test the 
alternate configuration interface. The experiment flow will be the same across all 
sets of experiments, with the fact that the configuration interface will be altered 
across sets.

The experiment begins with the participants being informed that they are in a
simulated censorship
environment, where some --- but not all --- websites are blocked. We will
instruct them to visit a non-blocked website and a blocked website on a
``standard'' browser (one that is not used for censorship circumvention, such
as Chrome, Safari, or Firefox) to illustrate the situation.
Then, the participants will find out the role they they will be playing in the study.
This role is that of a regular citizen, who is trying to visit blocked websites
for non-critical leisurely purposes,
and that there is a minimal chance of risk. This information is given
to achieve
consistency across participants: their behavior might be different if they were
visiting websites to accomplish a critical task, or if they knew that there
were great risks.
